Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-05 paper/paper.tex
small edits

\emph{Key Findings.}~The list of findings of this work includes--1)
Not only multiple different implementations can be leveraged in
differential testing, but differences in test suites can also be
important. 2) Even for problems with fairly clear specifications, as
in \javascript{}, there is likely to be (a lot of) variation between
different implementations. 3) Differential testing is feasible on
real, complex, widely used pieces of
software. Section~\ref{sec:lessons} expands and elaborates key
findings and lessons learned.

>>>>

\emph{Key Findings.}~We found that--1)~Differential testing and Test
Transplation are practical and effective techniques to find bugs on real,
complex, and widely used software systems, 2)~Even for problems with
fairly clear specifications, as in \javascript{}, there is likely (a
lot of) variation between different implementations, which brings instrinsic
challenges to developers that work on them.
Section~\ref{sec:lessons} expands and elaborates key
findings and lessons learned.
